### 2023-03-27 seitan/seitan.tex
some important changes

It's early June 2021, and you are M*d Mex Big Burrito Restaurant Group restaurant.
%
In Shadyside Pittsburgh Appalachia USA
you serve the canonical implementation of seitan wings.
If the NIST standards committee filed an entry for the food, they would surely enshrine one of yours.

@@

You are one of the first stops they make,
a high honor in the book of a foodie ex-grad student who knows the East End inside and out
(friends in tow, of course).
They have practiced Chapter 2's secret lost art, but something is still wrong,
and sitting at your table in the summer heat they realize what it is:
technique aside, even fully cooked, their dough recipe produces a chewy, glutinous inside,
whereas your wings are perfectly soft inside;
one's teeth pierce the fried shell and sink effortlessly through to the other side
in a delightful textural contrast.
They do not know how to replicate it, and at this point are too invested in the narrative to just ask.

They stay for three weeks in a ThursDz friend's guest room, only a little jealous of his homeownership.
They tell him the preceding 2 chapters, and together they make what is known so far.
He agrees it's too chewy.

@@

Cooking, baking, working matter with one's hands, is a wonderful grounding activity,
and your texture, your tenderness is perfect.

@@

\chapter{5}{Wing}

@@

%It's the first time you've seen them since quarantine, and
You have a lot to catch up on.
Where there was border collie Louie, there is now border collie Junior.
You are teaching your mom to play Heaven's Vault,
your new favorite conlang-learning archaeology VN,
trying to tell her that the helplessness the game makes her feel is in fact diagetic,
and she (also a language nerd) is kinda actually getting it.
%
Your psychological association is still tenuous,
because your gender is new to them and your body is new to all three of you,
but your parents will get there someday, beyond the scope of this work.

@@

\vspace{24em}

@@

\noindent \begin{tabular}{p{0.95\textwidth}}
	{\bf Ingredients (Wing; dry)} \\
	\hline
	{\em 14 oz} -- Vital wheat gluten \\
	{\em 1 oz} -- Nutritional yeast (or parmesan) \\
	{\em 3 Tbsp} -- Spices: rosemary, thyme, onion or garlic powder, and white pepper \\
	{\em 2 tsp} -- Salt \\
	\\
	{\bf Ingredients (Wing; wet)} \\
	\hline
	{\em 12 oz} -- Water (or chicken stock, for irony) \\
	{\em 6 oz} -- Tomato paste \\
	{\em 2 oz} -- Olive oil \\
	\\
	{\bf Ingredients (Buffalo)} \\
	\hline
	{\em 2 Tbsp} -- Butter (omit for vegans) \\
	{\em 2 Tbsp} -- Hot sauce (Frank's is canonical, but they prefer Cholula) \\
	\\
	{\bf Ingredients (Bluech)} \\
	\hline
	{\em 1/3 cup} -- Blue cheese (a nice, creamy pungent one from Penn Mac) \\
	{\em 1/3 cup} -- Buttermilk (you can substitute but it really makes a difference) \\
	{\em Spoonful} -- Plain greek yogurt or sour cream, for consistency, optional \\
	\\
	{\bf Method} \\
	\hline
\setlength{\parskip}{0.5em}
	In two bowls, separately mix the dry and wet wingredients. Combine and knead for about 5 minutes, until coherent but also tears easily. Add more liquid or gluten as necessary, a little at a time.

>>>>

It's early June 2021, and you are M*d Mex Big Burrito Restaurant Group restaurant.
%
You serve the canonical implementation of seitan wings
in Shadyside Pittsburgh Appalachia USA.
If the NIST standards committee filed an entry for the food, they would surely enshrine one of yours.

@@

You are one of the first stops they make
(friends in tow, of course),
a high honor in the book of a foodie ex-grad-student who knows the East End inside and out.
They have practiced Chapter 2's secret lost art, but something is still wrong,
and sitting at your table in the summer heat they realize what it is:
technique aside, even fully cooked, their dough produces a chewy, glutinous inside,
whereas your wings are perfectly soft;
one's teeth pierce the fried shell and sink effortlessly through to the other side
in a delightful textural contrast.
They do not know how to replicate it, and at this point are too invested in the narrative to just ask.

They stay for three weeks in a ThursDz friend's guest room, only a little jealous of his homeownership.
They tell him the preceding 2 chapters, and together they make what is known so far.
He likes it, but agrees it's too chewy.

@@

But cooking, baking, working matter with one's hands, is a wonderful grounding activity,
and your texture, your tenderness is perfect.

@@

\chapter{5}{Synthesis}

@@

%It's the first time you've seen them since quarantine, and
You have a lot to catch up on.
Where there was border collie Louie, there is now border collie Junior.
You will never know if Louie could tell you smell different now.
You are teaching your mom to play Heaven's Vault,
your new favorite conlang-learning archaeology VN,
trying to tell her that the helplessness the game makes her feel is in fact diagetic,
and she (also a language nerd) is kinda actually getting it.
%
Your psychological association is still tenuous,
because your gender is new to them and your body is new to all three of you,
but your parents will get there someday, beyond the scope of this work.

They take you on their traditional morning walk. % along the beach.
You always preferred the snow to the beach,
%but you come to understand why your mom does,
but you still relish the feeling of sand in your toes and saltwater lapping at your calves.
You had not felt the ocean on them since you made them yours.
You walk Junior and you get seafood together from a stall along the boardwalk
and suddenly the city of your birth feels like a bubble of immunity to that disaffected-millenial grief you carry everywhere else you go.

@@

\vspace{15em}

@@

\noindent \begin{tabular}{p{0.95\textwidth}}
	{\bf Ingredients (Wing; dry)} \\
	\hline
	{\em 14 oz} -- Vital wheat gluten \\
	{\em 1 oz} -- Nutritional yeast (or parmesan) \\
	{\em 3 Tbsp} -- Spices: rosemary, thyme, onion or garlic powder, and white pepper \\
	{\em 2 tsp} -- Salt \\
	\\
	{\bf Ingredients (Wing; wet)} \\
	\hline
	{\em 12 oz} -- Water (or chicken stock, for irony) \\
	{\em 6 oz} -- Tomato paste \\
	{\em 2 oz} -- Olive oil \\
	\\
	{\bf Ingredients (Buffalo)} \\
	\hline
	{\em 2 Tbsp} -- Butter (omit for vegans) \\
	{\em 2 Tbsp} -- Hot sauce (Frank's is canonical, but you prefer Cholula) \\
	\\
	{\bf Ingredients (Bluech)} \\
	\hline
	{\em 1/3 cup} -- Blue cheese (a nice, creamy, pungent one from Penn Mac) \\
	{\em 1/3 cup} -- Buttermilk (you can substitute but it really makes a difference) \\
	{\em Spoonful} -- Plain greek yogurt or sour cream, for consistency, optional \\
	\\
	{\bf Method} \\
	\hline
\setlength{\parskip}{0.5em}
	In two bowls, separately mix the dry and wet wingredients. Combine and knead for 5-10 minutes, until coherent but also tears easily. Add more liquid or gluten as necessary, a little at a time.
